01 - TreehopperFitness: Defining strategies and calculating frequencies

### 2023-07-23 scripts/Publilia-02-strats.Rmd
Updated visit vs early desertion figure for manuscript
minor changes to facet text

(guarding_durations_plot_2023 <- visited_1st_4d_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  mutate(`visited in 4 days` = 
           ifelse(`visited in 4 days` == "Visited", 
                  "Visited within first 4 days", 
                  "Not visited within first 4 days")) %>%
  ggplot(aes(x=guard_duration, fill=ants)) +
  geom_histogram(binwidth = 4) +
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Number of females") +
  scale_y_continuous(breaks = c(0,4,8),
                     labels = label_number(accuracy = 1)) +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1) +
  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
                     strip = hist_strips) +
  theme(strip.background = element_rect(color = NA),
        legend.justification = c(1,1),
        legend.position = c(1,0.2)) +
  geom_text(data = hatch_text,
            aes(x = 20, y = Inf, label = label),
            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
  coord_cartesian(clip = "off"))
```

>>>>

base_text <- expand.grid(ants = c("Ants removed", "Control"),
            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
                                    "Visited\nwithin first 4 days")) %>%
  tibble()

hatch_text <- base_text %>%
  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
         "Hatch date", 
         ""))

(guarding_durations_plot_2023 <- visited_1st_4d_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  mutate(`visited in 4 days` = 
           ifelse(`visited in 4 days` == "Visited", 
                  "Visited\nwithin first 4 days", 
                  "Not visited\nwithin first 4 days")) %>%
  ggplot(aes(x=guard_duration, fill=ants)) +
  geom_histogram(binwidth = 4) +
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Number of females") +
  scale_y_continuous(breaks = c(0,4,8),
                     labels = label_number(accuracy = 1)) +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1) +
  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
                     strip = hist_strips) +
  theme(strip.background = element_rect(color = NA),
        strip.text = element_text(size = 12),
        legend.justification = c(1,1),
        legend.position = c(1,0.2),
        legend.text = element_text(size = 12)) +
  geom_text(data = hatch_text,
            aes(x = 20, y = Inf, label = label),
            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
  coord_cartesian(clip = "off"))
```

# 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha
Sarah asked to remove the stats text
```{r, fig.width=3, fig.height=2}
Fig1_v1D +
  xlab("Day first visited (days from initiation)") +
  ylab("Guard duration of initiating female") +
    theme(legend.position = "none")
```
